### 2014-04-16 brains-protocol.tex
Update correlation figures, maybe needs further filtering, and text needs to be updated

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Correlations in the initial set of features \rk{show non-log version?} \cam{if we use log variables I guess we should show correlations on log variables -- I'm surprised by the level of correlation b/n (aoa) and (log PR), though}}
    \label{fig:feature-corrs-initial}
\end{figure}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.788\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Correlations in the filtered set of features \rk{show non-log version?}}
    \label{fig:feature-corrs-filtered}
\end{figure}

>>>>

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Spearman correlations in the initial set of features}
    \label{fig:feature-corrs-initial}
\end{figure}

\rk{Correlation talk needs to be redone for new set of features}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.788\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Spearman correlations in the filtered set of features \rk{further remove FA betweenness?}}
    \label{fig:feature-corrs-filtered}
\end{figure}
